Stochastic Wind Power Forecasting

### 2020-05-24 LaTeX_Code/Paper/paper_1line.tex
Mote detaills in the paper

Let $\{\Delta v_{j,i}\}_{j=1,i=1}^{M,N}$ be the set of error observation transitions, and $\psi(\Delta v_{j,i};\bm{\theta})$ the Lamperti transform for the transitions. The transformed observations transitions $\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}$ depend on the parameter $\bm{\theta}$.\\
The problem of maximizing the  $$\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}\right),$$
is not totally defined as the data $\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}$ depend on $\bm{\theta}$. However, we propose to find a fixed point $\bm{\theta}^*$ such that
\begin{equation}
\bm{\theta}^*=\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right).
\label{FP}
\end{equation}
{\color{red}In this point, the likelihood has a maximum for the data set corresponding to that point. (HOW CAN WE WRITE THIS BETTER?)}
We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
\begin{equation*}
\bm{\theta}^*-\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right)=0.
\end{equation*}
Given $\bm{\theta}^*=(\theta_0^*,\alpha^*)$, we call $\bm{\theta}^{**}=(\theta_0^{**},\alpha^{**})$ to the solution of
\begin{equation*}
\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right).
\end{equation*}
For each $\bm{\theta}^*$, we define the relative error function
\begin{equation}
\Psi(\bm{\theta}^*)=\frac{|\theta_0^{*}-\theta_0^{**}|}{|\theta_0^{*}|}+\frac{|\alpha^{*}-\alpha^{**}|}{|\alpha^{*}|},
\label{eq:rel_error}
\end{equation}
and remark that $\bm{\theta}^*$ is a fixed point if and only if $\Psi(\bm{\theta}^*)=0$.

@@

{ \color{red} Show that 24h is enough to ensure independence?}
All the following results involving a single provider refer to Provider A. Following the instruction for the initial guesses from section $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.

@@

As an auxiliary verification, we plot the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) as a function of the parameters, and we use extra minimization functions from MATLAB R2019b.

@@

As we are working in a low dimensional space, we can evaluate the relative error function (\ref{eq:rel_error}) in all the space of interest.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
\caption{Relative error function's level sets.}
\label{fig:neg-LLL}
\end{figure}
In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets for the relative error function (\ref{eq:rel_error}). The center deep green band is the set $\mathbb{A}$ such that $\Psi(\bm{\theta})<0.1$ if $\bm{\theta}\in\mathbb{A}$, it is the set of fixes-points candidates. The set of fixed-points candidates which also satisfies the condition of lying over the line $\theta_0\alpha=0.097$ is non-empty, i.e., $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.097\}\neq\emptyset.$$
We observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.097$ from the error SDE. We choose $(\theta_0^L,\alpha^L)=(2.45,0.040)$.\\
{\color{red}We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".}\\
\quad\\
To verify and compare this two vector of parameters, (i.e., $(\theta_0^E,\alpha^E)$ and $(\theta_0^L,\alpha^L)$), we simulate error paths in the $V-$space. We simulate five error paths for each day in the test set and construct histograms with the transitions. The histoframs can be seen in Figure (\ref{fig:hists}).

@@

After calibrating Model 2 on the training set using the complete likelihood (\ref{eq:complete_LH}), we can generate simulations of the wind power production for the time horizon of interest. Figure \ref{fig:simulation_paths} shows five simulated paths of the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/1.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/2.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/3.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/4.eps}
\caption{Five simulated wind power production paths using the approximate MLEs for Model 2 $(\theta_0, \alpha ,\delta)=(1.93,0.050,0.090)$. }
\label{fig:simulation_paths}
\end{figure}

On the basis of the approximate MLEs for Model 2, we can obtain empirical pointwise confidence bands for the wind power production. The next Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.

>>>>

Let $\{\Delta v_{j,i}\}_{j=1,i=1}^{M,N}$ be the set of error observation transitions, and $\psi(\Delta v_{j,i};\bm{\theta})$ the Lamperti transform for the transitions. The transformed observations transitions $\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}$ depend on the parameter $\bm{\theta}$.\\
The problem of maximizing the  $$\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}\right),$$
is not totally defined as the data $\{\Delta z_{j,i}\}_{j=1,i=1}^{M,N}$ depend on $\bm{\theta}$. However, we propose to find a fixed point $\bm{\theta}^*$ such that
\begin{equation}
\bm{\theta}^*=\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right).
\label{FP}
\end{equation}
{\color{red}In this point, the likelihood has a maximum for the data set corresponding to that point.}
We are interested in finding solutions for (\ref{FP}). If $\bm{\theta}^*$ solves (\ref{FP}), then
\begin{equation*}
\bm{\theta}^*-\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right)=0.
\end{equation*}
Given $\bm{\theta}^*=(\theta_0^*,\alpha^*)$, we call $\bm{\theta}^{**}=(\theta_0^{**},\alpha^{**})$ to the solution of
\begin{equation*}
\arg\max_{\bm{\theta}}\mathcal{L}_L\left(\bm{\theta};\{\psi(\bm{\theta}^*;\Delta v_{j,i})\}_{j=1,i=1}^{M,N}\right).
\end{equation*}
For each $\bm{\theta}^*$, we define the relative error function
\begin{equation}
\Psi(\bm{\theta}^*)=\frac{|\theta_0^{*}-\theta_0^{**}|}{|\theta_0^{*}|}+\frac{|\alpha^{*}-\alpha^{**}|}{|\alpha^{*}|},
\label{eq:rel_error}
\end{equation}
and remark that $\bm{\theta}^*$ is a fixed point if and only if $\Psi(\bm{\theta}^*)=0$.

@@

{ \color{red} Show that 24h is enough to ensure independence?}
All the following results involving a single provider refer to Provider A. Also, all calibrations involve the training sets and all simulations, the test sets. Following the instruction for the initial guesses from section $\ref{opt_sec}$, we obtain the initial guess $(\theta_0,\alpha,\delta)\approx(1.54,0.072,073)$.

@@

As an auxiliary verification, we plot the negative log-likelihood (negative version of (\ref{eq:loglikelihoodV})) as a function of the parameters, and we use additional minimization functions from MATLAB R2019b.

@@

{\color{red} This part still may change.} As we are working in a low dimensional space, we can evaluate the relative error function (\ref{eq:rel_error}) in all the space of interest.

\begin{figure}[H]
\centering
\includegraphics[width=0.7\textwidth]{../../MATLAB_Files/Results/likelihood/lamperti/Log-Likelihood.eps}
\caption{Relative error function's level sets.}
\label{fig:neg-LLL}
\end{figure}
In Figure (\ref{fig:neg-LLL}), we can see the numerical level sets for the relative error function (\ref{eq:rel_error}). The center deep green band is the set $\mathbb{A}$ such that $\Psi(\bm{\theta})<0.1$ if $\bm{\theta}\in\mathbb{A}$, it is the set of fixes-points candidates. The set of fixed-points candidates which also satisfies the condition of lying over the line $\theta_0\alpha=0.097$ is non-empty, i.e., $$\mathbb{A}\cap\{(\theta_0,\alpha):\theta_0\alpha=0.097\}\neq\emptyset.$$
We observe some possible candidates for fixed points, that also satisfies the empirical condition $\theta_0\alpha=0.097$ from the error SDE. We choose $(\theta_0^L,\alpha^L)=(2.45,0.040)$.\\
{\color{red}We interpret the set $\mathbb{A}$ as "the points where the transformation of the data, does not interfere with MLE".}\\
\quad\\
To verify and compare this two vector of parameters, (i.e., $(\theta_0^E,\alpha^E)$ and $(\theta_0^L,\alpha^L)$), we simulate error paths in the $V-$space. We simulate five error paths for each day in the test set and construct histograms with the transitions. The histograms can be seen in Figure (\ref{fig:hists}). We do not observe any particular change in the behavior of the solution for there parameters.

@@

After calibrating Model 2 on the training set using the complete likelihood (\ref{eq:complete_LH}), we can generate simulations of the wind power production for the time horizon of interest. Figure (\ref{fig:simulation_paths}) shows five simulated paths of the wind power production for each day of interest.

\begin{figure}[H]
\centering
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/1.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/2.eps}\\
\quad\\
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/3.eps}
\includegraphics[width=0.45\textwidth]{../../MATLAB_Files/Results/paths_testing_days/optimal_value/withDate/4.eps}
\caption{Four arbitrary days with five simulated wind power production paths each. }
\label{fig:simulation_paths}
\end{figure}
On the basis of the approximate MLEs for Model 2, we can obtain empirical pointwise confidence bands for the wind power production. Figure \ref{fig:confidence_bands} shows the empirical pointwise confidence bands for the wind power production for each day of interest, assuming Model 2 specification and a given forecaster.
